---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# lutzimporttest

<!-- badges: start -->
[![R-CMD-check](https://github.com/ateucher/lutzimporttest/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/ateucher/lutzimporttest/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of lutzimporttest is to test the importing of sf, which is a suggested package
in lutz, in a package which depends on lutz so that the "accurate" method of `lutz::tz_lookup()` is possible.

The lutz package has the {sf} package in `Suggests`, and only uses {sf} functions
conditionally when using the "acccurate" method, and checks that {sf} is installed
first. Because {sf} is in `Suggests`, it does not get installed automatically when
lutz is installed, which makes it tricky for a pacakge that depends on lutz to
use the functionality which depends on {sf} (`tz_lookup(..., method = "accurate")`).
The approach here is to include {sf} in `Imports` so that {sf} is installed
automatically in the reverse dependency that requires it. The issue is that
because {sf} functions are not called directly by the reverse dependency, `R CMD
check` complains about unused imports. The solution is to include a call to any
{sf} function in a "stub" function that is never actually used in the package.
This function is called `ignore_unused_imports()`.

## Installation

You can install the development version of lutzimporttest from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("ateucher/lutzimporttest")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(lutzimporttest)
use_lutz(48.5, -116.3)
```
